A Fully Decentralized Infrastructure for Subscription-based IoT Data Trading

### 2020-07-29 paper.tex
Update Conclusion to blockchain2020 and add Future Work section

\title{A Fully Decentralized Infrastructure for Subscription-based IoT Data Trading}
% Chinese title: 針對物聯網訂閱型資料交易的去中心化基礎建設

@@

% SaaS
The economic incentive model in our proposed IoT data trading platform works as subscription service that valuates the payments by data usage. The subscription-based models (e.g. SaaS and platform-as-a-service (PaaS)) are embedded in our lives, such as newspaper, video/audio streaming and softwares, which can bring enormous operating incomes and offer advantages that allows service providers have the flexibility in resource planning as well as a better prediction of revenue streams. And for service consumers, they can subscribe and unsubscribe the services at will at anytime. The subscription-based model can easily adapt the underlying pub/sub communication model and benefit both data providers and consumers which promotes a good circulation of the platform. In \cite{SaaS}, the author pointed out that the strength of the relationships between consumers and providers of subscription-based services depend on the service quality (i.e., the data quality in data trading platform), and trust is key to successful subscription-based services.

%trustless & automated
%trust: 對系統、對身份、對資料
In data trading platforms, there are three major aspects that need trust: identity, data ownership and trading. Proving the identity as well as the ownership of data are challenging issues among various roles in a large scale platform. In current systems, trusted third-party authority like CA is widely adopted to certify each member. However, building trust upon CA is dangerous and fragile. The compromise of routers or CA can break the trust of entire system, and the data portability of using third-party services is still under suspicion. Meanwhile, these concerns are taking into data storage as well, keeping data assets in a centralized data storage or cloud service meet the constraints of data portability, which may violate General Data Protection Regulation (GDPR)\cite{GDPR}. Besides CA and storage, the subscription history of data consumer may reveal his/hers interests and the exposure of personal information during trading process against GDPR as well. The final trust is trading procedures, apart from setting up the agreement between providers and consumers, both of them need to confirm that the agreement will be executed even if one party fails to comply.

Among the challenges of data trading platform\cite{BigDataMarket} and the requirements mentioned above, we conclude the following five essential ones:
\begin{itemize}
	\item \textbf{Scalability}. 
1) The performance of the platform should scale with the massive amount of participants. 2) The keys and entry points of data products managed by participants should be as small as possible. 
	\item \textbf{Integrity}. 1) Prevent unauthorized modifications. 2) Ensure the accuracy and validity of contents.	
	\item \textbf{Confidentiality}. 
1) Only the authorized participants can access data streams. 2) Legitimate participants can always retrieve data even if they're dropped from the network.	
	\item \textbf{Privacy}. Avoid revealing sensitive information of all participants, such as IP address and data consumers' habits which may leak within the subscription history.
	\item \textbf{Economics Incentive}. The economic incentives can encourage the data providers to participate in the system and pay more attention to the quality control. 
\end{itemize}

Taking all the requirements and the features of streaming data into consideration, the data trading platform for IoT towards a decentralized and trustless design. In this paper, we investigate the use of decentralized publish/subscribe (pub/sub) model and DLTs to construct the authority-less and trusted infrastructure. See Fig.~\ref{fig:system_design}. The pub/sub model features the scalability and resource-efficiency, and DLTs resolve the trust of the service, since data and contracts (i.e., smart contracts) written on DLTs are transparent, immutable, and enforced automatically, the digital rights of participants are protected. Lastly, an end-to-end encrypted transmission protocol built on top of DLT is used as data storage, which not only ensures the data integrity, but also enables access control and provides a scalable key and data management.

\subsection{Contributions}
The contributions in the paper are summarized as follow:
\begin{itemize}
	\item We investigate the usage of DLTs and distributed data storages in order to propose a decentralized architecture for IoT trading, and to enable participants to automate the trading procedures and secure digital assets exchange across different organizations.
	\item We apply the subscription-based services economic model to adapt the features of IoT streaming data, and clarify the importance of using a decentralized identity system for trading.
	\item We evaluate the performance and concerns of adopting an end-to-end encrypted transmission protocol, and propose an alternative approach for low-level devices to adopt this protocol while ensure the privacy of using the protocol.
	\item We analyze the cost of designed smart contract to estimate the minimum data product price for data providers to sustain a product and the minimum cost for data consumers to interact with date product.
\end{itemize}

@@

A. Colman et al. \cite{TrustedMarketplaceWearable} discussed on trading the sensitive data among wearables. Several security issues are well discussed and solved with DLTs in the paper, the system consists of multiple components aiming for different responsibilities, such as data anonymizer eliminates keen information for privacy protection, access controller handles the key management and contract manager manages Ethereum smart contracts. While the trading processes are split into multiple servers, and the request/response communication model is applied, the scalability problem of the marketplace remains.

In the following researches, Masked Authenticated Messaging (MAM)\cite{MAM} is regarded as a secure data transmission layer and data storage built on top of DLT which provides access control, tamper-proof and authentication functionalities by tailoring messages to a channel. Jinzhi Lu et al.\cite{luDecentralizedDM} builds the data exchange system with MAM and IPFS\cite{IPFS}, a content-based addressing distributed storage system. Considering the limited transaction processing capability of DLT, the authors suggest to adopt IPFS to handle the encrypted large data sets, then add the encrypted IPFS link to MAM for further exchange. This research takes MAM as data transmission layer only that focuses on secure data exchanging architecture design and security analysis, but the trading strategies are not studied yet. A similar infrastructure proposed by Zichichi et al.\cite{SocialGood} offered a key and entry points management with MAM that minimize the information which data producers need to hold. Also, Ethereum smart contract is used to maintain an authorized user list and to enable trading. However, the access control is examined by Authentication Service, the only client/server communication architecture, where the security issues and bottleneck of system emerges from, and the details of trading and interactions between providers and consumers are not illustrated in this paper. Though taking IPFS as data storage instead of MAM is more efficient due to the current growth of underlying DLT, the chance of data losses and the effeciency of IPFS remain, which will be further discussed in Section.~\ref{section:distributed_storage}.

@@

\subsection{Distributed Storage System}
\label{section:distributed_storage}
Decentralized storage systems allow users to store files in a distributed network that is maintained by individual nodes around the world instead of a central service provider. Nevertheless, DLTs are often used as the backbone of these systems as data storage and also an incentive layer to encourage people get involved in the network.

Filecoin \cite{FileCoin} in Inter-Planetary File system (IPFS) is an incentive layer to incent nodes to provide storage. IPFS is a content-based addressing storage model in a peer-to-peer network, which users can obtain the data with the unique hash value through the network. Furthermore, considering the data may loss in the network, IPFS provides \textbf{pin} command for users to store the contents locally that will not be removed. However, the IoT sensor devices have limited space which is not appropriate to preserve generated data. Also, users can have a hard time finding the contents quickly if data is not widely available, the large amount of IPFS nodes and contents. Thus, several pinning services like Pinata provide multiple IPFS nodes around the world to pin users' contents and charge by the size and replicas of contents, and users can even join the dedicated network to speed up the retreiving process.

Sia\cite{Sia} splits the uploaded file into multiple data segments encrypted with the owner's private key, then cipher text is sent to the Sia nodes that rent the storage in Siacoin through smart contracts. Files are duplicated in multiple nodes to prevent data loss.

@@

\begin{itemize}
\item \textbf{Data Provider: }
Data providers are the ones that generate streaming data and set the data price based on the different types of data. Subscription fees can motivate data providers to maintain and improve the quality of data.
\item \textbf{Data Consumer: }
Data consumers are entities that are willing to buy data streams. As it is laborious to widely deploy devices to collect data from scratch and it is also difficult to find desired data sets, purchase is the fastest and efficient way to get the desired data sets.
\item \textbf{Broker: }
Brokers are responsible for building an agreement between data providers and consumers. Brokers are required to be online for providers and consumers, and they are incentivized by charging brokerage fees.
\end{itemize}

We adopt the brokered infrastructure for three reasons. Firstly, it inherits the benefits from the standard pub/sub model which is more efficient than the request/response model specifically in a large scale system. Furthermore, if either side is offline, the proceeding tasks have to stop and start over. With brokers, the unfinished work can be cached or accomplished. Second, a fully decentralized architecture has difficulties to brings data providers and consumers together, both of them need to reveal more sensitive information, such as IP address, in order to build the communication tunnel. The existence of brokers resolved the privacy issue, as brokers are the bridges that link data providers and consumers, participants can trade with minimum information like its identifier and public key. Third, a refund process needs brokers to host and supervise the procedures in order to protect the rights of participants, which will be further discussed in Section.~\ref{section:refund}.

\begin{figure*}[!t]
    \centering
    \includegraphics[width=\linewidth]{channel_and_key}
    \caption{Within MAM channel, the message publisher has 2 types of key, an encryption key for encrypting contents and a signature key per message for digital signatures. Subscribers can validate the message with signature keys and decrypt messages with encryption keys.}
    \label{fig:channel_and_key}
\end{figure*}

@@

\subsection{Digital Identity}
The digital identity represents entities and holds the digital assets within the digital world, it is important to prove and show the identity to others during interactions. We select the decentralized identity model rather than a centralized one for the concerns in Table.\ref{tab:did}.

@@

Through TangleID, entities get a public/private key pair, the location of DID document and the seed (i.e., the identifier of its owner in IOTA) that used to generate the DID document MAM channel. The public/private key pair can be used to exchange sensitive data and establish the trust communication, where messages that are encrypted with a public key can only be decrypted with private key owner. During data subscription process, the encryption keys of data products are encrypted with data consumers' public key on DID document which ensures only the subscribed consumers are accessible. See Fig.~\ref{fig:TangleID}

@@

\subsection{Enable Automated Trading Process}
\begin{figure*}[t]
    \centering
    \includegraphics[width=4in]{smart_contract_mam}
    \caption{The information of identity and data streams are stored on the Tangle with MAM which are all recorded on Product Contracts. Participants can easily retrieve information via Product Contract and proceed trading. For signature validation check and further exchange encryption keys, the MAM channel ID of participants' DID document are written down, presented in blue color. The orange color stands for the information of data products, which includes the data stream channel/endpoint ID.}
    \label{fig:smart_contract_mam}
\end{figure*}

@@

With the functionalities of Ethereum smart contracts, a flexible and verifiable trading mechanism can be achieved. In our system, \textbf{Product Contract} is made for the product launching and trading. The information of data products such as address of the data provider, subscription fee, brokerage fee, threshold of consent votes of refunding, MAM channel/endpoint ID (the data entry point), time period and the broker-verified encryption key are listed on Product Contract. Listing. \ref{lst:constructor} list the data fields of Product Contract, and Fig.~\ref{fig:smart_contract_mam} shows the relationship of Product Contract and MAM. Furthermore, the participants can exchange encryption keys without any authorities via smart contracts. Though this design may cost extra transaction fees than exchanging key off-chain, it is considered a more secure strategy to protect the privacy of participants that only the DID document address and Ethereum addresses are revealed during the subscription process.

The transparency of smart contracts bring advantages for data providers and consumers. One of the advantage is that the trading states and progress are visible and verifiable which profits providers and consumers respectively. For data providers, with every detail opened, the consumer list functions like a reputation evaluation, the better the quality the more the consumers he/she has, which are also reputation references for data consumers.

@@

\subsection{Enable computation tasks delegation to broker with privacy}
To manage data products and to benefit from trading, data providers have to interact with MAM and Ethereum smart contract while doing its original tasks. However, the limited resources of low-level devices should be used on its jobs instead of handling all trading processes. Therefore, the operations of MAM and smart contracts are better to be delegated to brokers.

The delegation should ensure the privacy of data providers, for instance, brokers are asked to attach messages to MAM without knowing the contents as well as record encryption keys to smart contracts. To record encryption key to smart contract, data provider computes the digest of sensitive contents with hash function, and sends the digest as well as the signature to brokers. Broker can first verify the signature from data provider with the public key on DID document. If it's valid, then the broker uploads the key; otherwise the process will be aborted. Note that the broker needs to sign the encrypted encryption key he/she receives proving that it is uploaded by the responsible broker. This procedure allows data consumers to check whether the encryption key is uploaded by committed data provider and broker before subscription. Fig.~\ref{fig:key_upload} demonstrates the key uploading process to Product Contract via a broker.

\begin{figure}[h]
    \centering
    \includegraphics[width=3.5in]{key_upload}
    \caption{To add encryption key to Product Contract, the data provider sends the digest of encryption key and the one that signed with his/hers private key. After the broker receive the request, he/she performs digital signature as well to prove the ecryption key is uploaded by the responsible broker, then writes the result to the Product Contract.}
    \label{fig:key_upload}
\end{figure}

@@

\subsection{The Advantages of Adopting MAM in Subscription-based Data Trading Infrastructure}
%scalability
\subsubsection{A Scalable Keys and Data Entry Points Management}
The importance of scalable key and data entry points management increases over time. In MAM, with an entry point (i.e., the address of transaction) and the encryption key, one can derive the following addresses of transaction and retrieve data. To manage a data stream, the owner only needs to preserve 1 entry point and 1 encryption key in MAM, but $N$ entry points and 1 encryption key in other distributed storage.

%classify
\subsubsection{Data Sreams Classification and Traceability}
The channel and endpoint structures enable users to be able to easily categorized data streams with respect to different types and usages. For instance, sensor devices like AirBox\cite{LASS}, collects environmental data, can split the statistics like PM 2.5 and humidity by time period into separate channels, which is useful for data providers to organize records and to pack into different data products. As for data traceability, users can easily track the footprints of data change logs as well as checking the validity of modifications with the signature.

@@

\section{Decentralized Subscription-based Data Trading Models}
\label{section:trading_model}
In this section, we illustrate how participants can join the data subscription platform, start subscribing, cancel subscription, and request refund.

@@

\subsection{Launch a Refund}
Data subscription is a high risk which data provider may not upload data as the agreement set after receiving the subscription fee. Therefore, in our proposed architecture, data consumers can trigger a refund procedure by sending a transaction on Ethereum if the data is not available or defective. When the refund procedure is launched, all consumers vote to decide whether the refund is established. See Fig.~\ref{fig:refund}. Once the ratio of consent votes of refunding is higher than a threshold, the subscription fee is proportionally transferred to the data provider, broker and every consumer as following, where $N$ is the number of consumers in this contract:

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=1.5in]{refund}
    \caption{Once a data consumer launch a refund vote, all consumers start voting to decide whether they want a refund. Finally, the establishment of refund is determined by Product Contract after checking the number of votes is larger than a threshold or not.}
    \label{fig:refund}
\end{figure}

However, refund conditions are complicated in the subscription services in the real world, participants can launch a refund in following conditions: First, as proposed methods above, consumers launch a refund vote when the data provider does not upload data as expected after receiving the subscription fee. Nevertheless, multiple issues still need to be investigated such as, consumers can only initiate a refund after getting the data or in a certain time period, the broker should host and set a vote timeline to count the votes, and handling the condition that not enough consumers join the vote need to be considered carefully. Second, brokers operate the subscription platform by earning brokerage fee, which is a deal between brokers and providers. If they can not reach a consensus of the brokerage fee during subsription period, brokers can launch a refund and refuse to handle the product. Third, the refund could launch by providers when they fail to maintain products as committed.

@@

\section{Conclusions}
\label{section:conclusion}
By combining the established standards and openly-developed specifications, this paper proposed an autonomous publish/subscribe model design to serve as a vendor and industry-neutral platform, automating the trading of digital assets and services. It was built with blockchain network, immutable audit trails, and contracts with an integrated decentralized identity system, to ensure the authenticity of all participants, enable secure communication and flexible trading mechanisms.

In the subscription-based data trading, there are some issues that worth discussing and improving. Firstly, reduce the Gas usage of trading models, as we mentioned in Section~\ref{section:smart_contract_evaluation}, the key exchange process consumes a lot of Gas due to the frequent store operation. Therefore, it is worth discussing that how zero-knowledge protocol could used to exchange key with lower cost, and even validate the key within transfers. Second, brokers are the key to operating a stable system, since they are irreplaceable either from the view of architecture design or trading procedures. However, the issues such as the minimum number of brokers needed to operation the system, and the evaluation of adopting gossip protocol among brokers to gossipped trading status, which enables other brokers to handle trading process when on crashed.

>>>>

\title{A Fully Decentralized Infrastructure for Subscription-based IoT Data Trading}
% Chinese title: 針對物聯網資料交易的去中心化基礎建設

@@

% SaaS
The economic incentive model in our proposed IoT data trading platform works as subscription service that valuates the payments by data usage. The subscription-based models (e.g. SaaS and platform-as-a-service (PaaS)) are embedded in our lives, such as newspaper, video/audio streaming and softwares, which can bring enormous operating incomes and offer advantages that allows service providers have the flexibility in resource planning as well as a better prediction of revenue streams. And for service consumers, they can subscribe and unsubscribe the services at will at anytime. The subscription-based model can easily adapts the underlying pub/sub communication model and benefit both data providers and consumers which promotes a good circulation of the platform. In \cite{SaaS}, the author pointed out that the strength of the relationships between consumers and providers of subscription-based services depends on the service quality (i.e., the data quality in data trading platform), and trust is key to successful subscription-based services.

%trustless & automated
%trust: 對系統、對身份、對資料
In data trading platforms, there are three major aspects that need trust: identity, data ownership and trading. Proving the identity as well as the ownership of data is a challenging issue among various roles in a large scale platform. In current systems, trusted third-party authority like CA is widely adopted to certify each member. However, building trust upon CA is dangerous and fragile. The compromise of routers or CA can break the trust of entire system, and the data portability of using third-party services is still under suspicion. Meanwhile, these concerns are taking into data storage as well, keeping data assets in a centralized data storage or cloud service meet the constraints of data portability, which may violate General Data Protection Regulation (GDPR)\cite{GDPR}. Besides CA and storage, the subscription history of data consumer may reveal his/hers interests and the exposure of personal information during trading process against GDPR as well. The final trust is trading procedures, apart from setting up the agreement between providers and consumers, both of them need to confirm that the agreement will be executed even if one party fails to comply.

Among the challenges of data trading platform\cite{BigDataMarket} and the requirements mentioned above, we conclude the following four essential ones:
\begin{itemize}
	\item \textbf{Scalability}. 
1) The performance of the platform should scale with the massive amount of participants. 2) The keys and entry points of data products managed by participants should be as small as possible. 
	\item \textbf{Integrity}. 1) Prevent unauthorized modifications. 2) Ensure the accuracy and validity of contents.	
	\item \textbf{Confidentiality}. 
1) Only the authorized participants can access data streams. 2) Participants that have access can always retrieve data even if they're dropped from the network.	
	\item \textbf{Privacy}. Avoid revealing sensitive information of all participants, such as IP address and data consumers' habits which may leak within the subscription history.
	\item \textbf{Economics Incentive}. The economic incentives can encourage the data providers to participate in the system and pay more attention to the quality control. 
\end{itemize}

Taking all the requirements and the features of streaming data into consideration, the data trading platform for IoT towards a decentralized and trustless design. In this paper, we investigate the use of decentralized publish/subscribe (pub/sub) model and DLTs to construct the authority-less and trusted infrastructure. See Fig.~\ref{fig:system_design}. The pub/sub model features the scalability and resource-efficiency, and DLTs resolve the trust of the service, since data and contracts (i.e., smart contracts) written on DLTs are transparent, immutable, and enforced automatically, which allows devices focus on their jobs while gaining the rewards. Lastly, an end-to-end encrypted transmission protocol built on top of DLT is used as data storage, which not only ensures the data integrity, but also enables access control and provides a scalable key and data management.

\subsection{Contributions}
The contributions in the paper are summarized as follow:
\begin{itemize}
	\item We investigate the usage of DLTs and distributed data storages in order to propose a decentralized architecture for IoT trading, and enables participants to automate the trading procedures and secure digital assets exchange across different organizations.
	\item We apply the subscription-based services economic model to adapt the features of IoT streaming data, and clarify the importance of using a decentralized identity system for trading.
	\item We evaluate the performance and concerns of adopting an end-to-end encrypted transmission protocol, and propose an alternative approach for low-level devices to adopt this protocol while ensure the privacy of using the protocol.
	\item We analyze the cost of designed smart contract to estimate the minimum data product price for data providers to sustain a product and the minimum cost for data consumers to interact with date product.
\end{itemize}

@@

A. Colman et al. \cite{TrustedMarketplaceWearable} discussed on trading the sensitive data among wearables. Several security issues are well discussed and solved with DLTs in the paper, the system consists of multiple components that has its different responsibilities, such as data anonymizer eliminates keen information for privacy protection, access controller handles the key management and contract manager manages Ethereum smart contracts. While the trading processes are split into multiple servers, and the request/response communication model is applied, the scalability problem of the marketplace remains.

In the following researches, Masked Authenticated Messaging (MAM)\cite{MAM} is regarded as a secure data transmission layer and data storage built on top of DLT which provides access control, tamper-proof and authentication functionalities by tailoring messages to a channel. Jinzhi Lu et al.\cite{luDecentralizedDM} builds the data exchange system with MAM and IPFS\cite{IPFS}, a content-based addressing distributed storage system. Considering the limited transaction processing capability of DLT, the authors suggest to adopt IPFS to handle the encrypted large data sets, then add the encrypted IPFS link to MAM for further exchange. This research takes MAM as data transmission layer only that focuses on secure data exchanging architecture design and security analysis, but the trading strategies are not studied yet. A similar infrastructure proposed by Zichichi et al.\cite{SocialGood} offered a key and entry points management with MAM that minimize the information which data producers need to hold. Also, Ethereum smart contract is used to maintain an authorized user list and to enable trading. However, the access control is examined by Authentication Service, the only client/server communication architecture, where the security issues and bottleneck of system emerges from, and the details of trading and interactions between providers and consumers are not illustrated in this paper.

@@

\subsection{Distributed Storage System}
Decentralized storage systems allow users to store files in a distributed network that is maintained by individual nodes around the world instead of a central service provider. Nevertheless, DLTs are often used as the backbone of these systems as data storage and also an incentive layer to encourage people get involved in the network. Filecoin \cite{FileCoin} in Inter-Planetary File system (IPFS) is an incentive layer to incent nodes to provide storage. IPFS is a content-based addressing storage model in a peer-to-peer network, which users can obtain the data with the unique hash value through the network. However, no cryptographic system is applied for user-uploaded files. Sia\cite{Sia} splits the uploaded file into multiple data segments encrypted with the owner's private key, then cipher text is sent to the Sia nodes that rent the storage in Siacoin through smart contracts. Files are duplicated in multiple nodes to prevent data loss.

@@

\begin{itemize}
\item \textbf{Data Provider: }
Data providers are the ones that generate streaming data and set the data price based on the different types of data. With the subscription fee that earned via trading, data providers are incentivized to maintain and improve the quality of data.
\item \textbf{Data Consumer: }
Data consumers are entities that are willing to buy data streams. As it is laborious to widely deploy devices to collect data from scratch, and without a marketplace, it is also difficult to find providers of the data sets, purchases is the fastest and efficient way to get the desired data sets.
\item \textbf{Broker: }
Brokers are responsible for building an agreement between data providers and consumers. Also brokers can represent data providers to perform computing tasks as brokers are expected to have higher resource.
\end{itemize}

We adopt the brokered infrastructure for three reasons. Firstly, it inherits the benefits from the standard pub/sub model which is more efficient than the request/response model specifically in a large scale system. Furthermore, if either side is offline, the proceeding tasks have to stop and start over. With brokers, the unfinished work can be cached or accomplished. Second, a fully decentralized architecture has difficulties to brings data providers and consumers together, both of them need to reveal more sensitive information, such as IP address, in order to build the communication tunnel. The existence of brokers resolved the privacy issue, as brokers are the bridges that link data providers and consumers, participants can trade with minimum information like its identifier and public key. Third, as brokers running on machines in a stable network and electricity environment, participants on resource-constrained devices can offload the computation tasks to brokers that enables a proxy server implementation mentioned in Section~\ref{section:ta_endpoint}. With the end-to-end encryption trasmission protocol we used, brokers can perform verifiable checks without knowing the contents.

\begin{figure*}[!t]
    \centering
    \includegraphics[width=\linewidth]{channel_and_key}
    \caption{Within MAM channel, the message publisher has 2 types of key, the encryption keys for content encryption and signature keys for digital signatures. Subscribers can validate the message with signature keys and decrypt messages with encryption keys.}
    \label{fig:channel_and_key}
\end{figure*}

@@

\subsection{Digital Identity}
The digital identity represents an entity and holds the digital assets within the digital world, it is important to prove and show the identity to others during interactions. We select the decentralized identity model rather than a centralized one for the concerns in Table.\ref{tab:did}.

@@

Through TangleID, entities get a public/private key pair, the location of DID document and the seed (i.e., the identifier of its owner in IOTA) that generates the DID document MAM public channel. The public/private key pair can be used to exchange sensitive data and establish the trust communication, where messages that are encrypted with a public key can only be decrypted with private key owner. During data subscription process, the encryption keys of data products are encrypted with data consumers' public key on DID document which ensures only the subscribed consumers are accessible. See Fig.~\ref{fig:TangleID}

@@

\subsection{Enable Automated Trading Process}
\begin{figure*}[t]
    \centering
    \includegraphics[width=4in]{smart_contract_mam}
    \caption{The information of identity and data streams are stored on the Tangle with MAM which are all recorded on Product Contracts. Participants can easily retrieve information via Product Contract and proceed trading. For signature validation check and further exchange encryption keys, the MAM channel ID of participants' DID document  are written down, presented in blue color. The orange color stands for the information of data products, which includes the data stream channel/endpoint ID and encryption key certified by broker.}
    \label{fig:smart_contract_mam}
\end{figure*}

@@

With the functionalities of Ethereum smart contracts, a flexible and verifiable trading mechanism can be achieved. In our system, \textbf{Product Contract} is made for the product launching and trading. The information of data products such as address of the data provider, subscription fee, brokerage fee, threshold of consent votes of refunding, MAM channel/endpoint ID (the data entry point), time period and the broker-verified encryption key are listed on Product Contract. Listing. \ref{lst:constructor} list the data fields of Product Contract, and Fig.~\ref{fig:smart_contract_mam} shows the relationship of Product Contract and MAM. Furthermore, the participants can exchange encryption keys without any authorities via smart contracts. Though this design may cost extra transaction fees than exchanging key off-chain, it is considered a more secure strategy to protect the privacy of participants.

The transparency of smart contracts bring advantages for data providers and consumers. One of the advantage is that the trading states and progress are visible and verifiable which profits providers and consumers respectively. For data providers, with every details opened, the consumer list functions like a reputation evaluation, the better the quality the more the consumers he/her has. The consumer list and the states of products, which includes \textit{Launched, KeyCertified, Finished} and \textit{Refunded} are key reputation referenced for data consumers to decide whether to subscribe.

@@

\subsection{Enable computation tasks delegation to broker with privacy}
To manage data products and to benefit from trading, data providers have to interact with MAM and Ethereum smart contract while doing its original tasks. However, the resources of low-level devices are precious which should be used to focus on its jobs. Therefore, the operations of MAM and smart contracts are better to be delegated to brokers.

The delegation should ensure the privacy of data providers, for instance, brokers are asked to attach messages to MAM without knowing the contents as well as record encryption keys to smart contracts. To record encryption key to smart contract, data provider computes the digest of sensitive contents with hash function, and sends the digest as well as the signature to brokers. Broker can first verify the signature from data provider with the public key on DID document. If it's valid, then the broker uploads the key, otherwise the process will be aborted. Note that the broker needs to sign the messages he/she receives, which has been proven to be key uploaded by a broker recorded on the Product Contract. The number of key uploading time is also restricted in order to avoid data provider uploading fake key frequently. If the data consumers find out the encryption key does not match the signature or can not decrypt data streams as expected, they can launch a vote refund to withdraw their funds. Fig.~\ref{fig:key_upload} demonstrates the key uploading process to Product Contract via a broker.

\begin{figure}[h]
    \centering
    \includegraphics[width=3.5in]{key_upload}
    \caption{To add encryption key to Product Contract, the data provider sends the digest of encryption key and the one that signed with his/hers private key. After the broker receive the request, he/she performs digital signature as well, then write the result to the Product Contract.}
    \label{fig:key_upload}
\end{figure}

@@

\subsection{The Advantages of Adopting MAM in Subscription-based Data Trading Infrastructure}
%scalability
\subsubsection{A Scalable Keys and Data Entry Points Management}
The importance of scalable key and data entry points management increases over time. In MAM, with an entry point (i.e., the address of transaction) and the encryption key, one can derive the following addresses of transaction and retrieve data. Table.~\ref{tab:mam_scalability} compares the key and addresses that need to be managed by using MAM and other distributed storage systems. Assuming the length of data stream is 7, and each record is encrypted with the same key. With MAM, only 1 key and 1 entry point is required while other distributed storage need to reserve 7 entry points for each data record.

\begin{table}[htbp]
	\caption{Number of keys and entry points of a data stream that need to managed with length 7.}
	\label{tab:mam_scalability}
	\begin{center}
	\begin{tabular}{|c|c|c|}
	\hline
		\textbf{Items} & \textbf{MAM} & \textbf{Others} \\ 
		\hline
		keys & 1 & 1 \\ 
		\hline
		entry points & 1 & 7 \\ 
		\hline
	\end{tabular}
	\end{center}
\end{table}

%classify
\subsubsection{Data Sreams Classification}
The channel and endpoint structures enable users to be able to easily categorized data streams with respect to different types and usages. For instance, a voice assistant can create a channel every day with multiple endpoints for each gadgets to record daily logs. Another example is sensor devices like AirBox\cite{LASS}, collects environmental data, can split the statistics like PM 2.5 and humidity by time period into separate channels, which is useful for data providers to organize records and to pack into different data products. To do the classification in other distributed storage also encounters the aforementioned scalability problem.

%data trace
\subsubsection{A Traceable Data Stream}
Data traceability is an important security issue that allows users to track the changes of data. Currently, hash is widely used to generate checksums of entire package of files, users can compare the hash value of files in order to check the integrity. Yet the hash values of each new version are unrelated and it's hard to point out the differences between versions. MAM benefits from the singly linked-list data structure which attaches messages chronologically, users can easily track the footprints of data change logs as well as checking the validity of modifications with the signature.

@@

\section{Decentralized Subscription-based Data Trading Case Study}
\label{section:trading_model}
In this section, we illustrate how participants can join the data subscription platform, start subscribing, cancel subscription, and request refund.

@@

\subsection{Launch a Refund}
Data subscription is a high risk which data provider may not upload data as the agreement set after receiving the subscription fee. Therefore, in our proposed architecture, data consumers can trigger a refund procedure by sending a transaction on Ethereum if the data is not available or defective. When the refund procedure is launched, all consumers vote to decide whether the refund is established. See Fig.~\ref{fig:refund}. Once the ratio of consent votes of refunding is higher than a threshold, the subscription fee is proportionally transferred to the data provider, broker and every consumer as following, where$N$ is the number of consumers in this contract:

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=1.5in]{refund}
    \caption{Once a data consumer launch a refund procedure, all consumers votes to decide whether they want a refund from data providers. Finally, the establishment of refund is determined by Product Contract after checking the votes is higher than a threshold or not.}
    \label{fig:refund}
\end{figure}

@@

\section{Conclusion}
\label{section:conclusion}
By combining the established standards and openly-developed specifications, this paper proposed a highly decentralized, autonomous publish/subscribe model design that combines data storage and trading together in order to ensure the digital rights of both data providers and consumers during the dynamic data streaming trading. It was built with blockchain network, immutable audit trails, and contracts with an integrated decentralized identity system, to enable the data stream trading by shifting risks from centralized services, ensure the authenticity of all participants, clarify the data ownership, enable secure communication and flexible trading mechanisms.

Compared to previous works, we 1.) identify a trustless data trading infrastructure, 2.) ensure the confidentiality of scalable IoT-based sensor data, and 3.) consolidate the economic incentives in the entire ecosystem. Meanwhile, we consider the heavy workload of the low-level sensors, conduct an experiment which authenticate the data providers to delegate the MAM operations to Tangle-accelerators, and conclude that the performance of the E2EE approach is more fitting than the MAM solution. In particular, this work discusses the workflow for subscription-based IoT data trading: Launching, subscribing, unsubscribing, and refund.

\section{Future Work}
In the subscription-based data trading, there are some issues that worth discussing and improving. Firstly, reduce the Gas usage of trading models, as we mentioned in Section~\ref{section:smart_contract_evaluation}, the key exchange process consumes a lot of Gas due to the frequent store operation. Therefore, it is worth discussing that how zero-knowledge protocol could used to exchange key with lower cost, and even validate the key within transfers. Second, brokers are the key to operating a stable system, since they are irreplaceable either from the view of architecture design or trading procedures. However, the issues such as the minimum number of brokers needed to operation the system, and the evaluation of adopting gossip protocol among brokers to gossipped trading status, which enables other brokers to handle trading process when on crashed.
